\let\negmedspace\undefined
\let\negthickspace\undefined
\documentclass[journal]{IEEEtran}
\usepackage[a5paper, margin=10mm, onecolumn]{geometry}
%\usepackage{lmodern} % Ensure lmodern is loaded for pdflatex
\usepackage{tfrupee} % Include tfrupee package

\setlength{\headheight}{1cm} % Set the height of the header box
\setlength{\headsep}{0mm}     % Set the distance between the header box and the top of the text

\usepackage{gvv-book}
\usepackage{gvv}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts,amsthm}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{txfonts}
\usepackage{listings}
\usepackage{enumitem}
\usepackage{mathtools}
\usepackage{gensymb}
\usepackage{comment}
\usepackage[breaklinks=true]{hyperref}
\usepackage{tkz-euclide} 
\usepackage{listings}
\usepackage{gvv}                                        
\def\inputGnumericTable{}                                 
\usepackage[latin1]{inputenc}                                
\usepackage{color}                                            
\usepackage{array}  
\usepackage{longtable}                                       
\usepackage{calc}                                             
\usepackage{multirow}                                         
\usepackage{hhline}                                           
\usepackage{ifthen}                                           
\usepackage{lscape}
\usepackage{multicol}
\begin{document}

\bibliographystyle{IEEEtran}
\vspace{3cm}

\title{GATE-2016-CE}
\author{AI24BTECH11025-P.L.Kushal}
% \bigskip
{\let\newpage\relax\maketitle}

\renewcommand{\thefigure}{\theenumi}
\renewcommand{\thetable}{\theenumi}
\setlength{\intextsep}{10pt} % Space between text and floats


\numberwithin{equation}{enumi}
\numberwithin{figure}{enumi}
\renewcommand{\thetable}{\theenumi}
\begin{enumerate}[start=40]

\item The porosity  $n$  and the degree of saturation $S$ of a soil sample are 0.7 and $40\%$, respectively. In a $100 \, \text{m}^3$ volume of the soil, the volume (expressed in $m^3$) of air is \underline{\hspace{2cm}}.\\
\item A homogeneous gravity retaining wall supporting a cohesionless backfill is shown in the figure. The lateral active earth pressure at the bottom of the wall is 40 kPa. 


\input{figs/fig1}





The minimum weight of the wall (expressed in kN per m length) required to prevent it from overturning about its toe (Point P) is  
\begin{multicols}{4}
\begin{enumerate}
\item 120 
\item 180
\item 240
\item 360
\end{enumerate} 
\end{multicols}




\item An undisturbed soil sample was taken from the middle of a clay layer (i.e., 1.5 m below GL), as shown in figure. The water table was at the top of clay layer. Laboratory test results are as follows:\\
\begin{flushleft}
    \begin{tabbing}
        \hspace*{3cm}\=\hspace*{4cm}\=\kill
        Natural water content of clay \> : \> 25\% \\
        Preconsolidation pressure of clay \> : \> 60 kPa \\
        Compression index of clay \> : \> 0.50 \\
        Recompression index of clay \> : \> 0.05 \\
        Specific gravity of clay \> : \> 2.70 \\
        Bulk unit weight of sand \> : \> 17 kN/m$^3$ \\
    \end{tabbing}
\end{flushleft}A compacted fill of 2.5 m height with unit weight of 20 kN/m$^3$ is placed at the ground level.
% diagram comes here

\input{figs/fig2}

 Assuming unit weight of water as 10 kN/m$^3$, the ultimate consolidation settlement (expressed in mm) of the clay layer is \underline{\hspace{3cm}}.\\
\item A seepage flow condition is shown in the figure. The saturated unit weight of the soil $\gamma_{\text{sat}} = 18 \, \text{kN/m}^3$. Using unit weight of water, $\gamma_w = 9.81 \, \text{kN/m}^3$, the effective vertical stress (expressed in kN/m$^2$) on plane X-X is \underline{\hspace{2cm}}.\\

\input{figs/fig3}
\item A drained triaxial compression test on a saturated clay yielded the effective shear strength parameters as $c' = 15 \, \text{kPa}$ and $\phi' = 22^\circ$. Consolidated Undrained triaxial test on an identical sample of this clay at a cell pressure of 200 kPa developed a pore water pressure of 150 kPa at failure. The deviator stress (expressed in kPa) at failure is \underline{\hspace{2cm}}.\\

\item A concrete gravity dam section is shown in the figure. Assuming unit weight of water as 10 kN/m$^3$ and unit weight of concrete as 24 kN/m$^3$, the uplift force per unit length of the dam (expressed in kN/m) at PQ is \underline{\hspace{2cm}}.\\

\input{figs/fig4}
\item Seepage is occurring through a porous media shown in the figure. The hydraulic conductivity values $k_1, k_2, k_3$ are in m/day. The seepage discharge (m$^3$/day per m) through the porous media at section PQ is  

\input{figs/fig5}

\begin{multicols}{4}
\begin{enumerate}
\item $\frac{7}{12}$
\item $\frac{1}{2}$
\item $\frac{9}{16}$
\item $\frac{3}{4}$
\end{enumerate} 
\end{multicols}

\item A 4 m wide rectangular channel, having bed slope of 0.001 carries a discharge of 16 m$^3$/s. Considering Manning's roughness coefficient = 0.012 and $g = 10 \, \text{m/s}^2$, the category of the channel slope is  (A) horizontal   (B) mild   (C) critical   (D) steep.
\begin{multicols}{4}
\begin{enumerate}
\item horizontal
\item mild
\item critical
\item steep
\end{enumerate} 
\end{multicols}
\item A sector gate is provided on a spillway as shown in the figure. Assuming $g = 10 \, \text{m/s}^2$, the resultant force per meter length (expressed in kN/m) on the gate will be \underline{\hspace{2cm}}.\\

\input{figs/fig6}
\item A hydraulically efficient trapezoidal channel section has a uniform flow depth of 2 m. The bed width (expressed in m)\\

\item Effluent from an industry 'A' has a pH of 4.2. The effluent from another industry 'B' has double the hydroxyl (OH) ion concentration than the effluent from industry 'A'. pH of effluent from the industry 'B' will be \underline{\hspace{3cm}}.\\

\item An electrostatic precipitator (ESP) with $5600 m^{2}$ of collector plate area is 96 percent efficient in treating 185 m$^{3}$/s of flue gas from a 200 MW thermal power plant. It was found that in order to achieve 97 percent efficiency, the collector plate area should be 6100 m$^{2}$. In order to increase the efficiency to 99 percent, the ESP collector plate area (expressed in m$^{2}$) would be \underline{\hspace{3cm}}.\\

\item The 2-day and 4-day BOD values of a sewage sample are 100 mg/L and 155 mg/L, respectively. The value of BOD rate constant (expressed in per day) is \underline{\hspace{3cm}}. \\

\end{enumerate}
\end{document}